### 2016-11-11 intro.tex
Added more intro

Understanding how galaxies form and evolve is therefore key to understanding the
origin of all the objects within them.

\section{The Cosmological Context of Galaxy Formation}
\section{Numerical Simulations of Galaxies}
\section{The Importance of Feedback}
\begin{figure}
    \includegraphics[width=\textwidth]{M82.eps}
    \caption{Massive outflows in M82}{The evidence for feedback is no clearer
    than here in the Cigar Galaxy, M82.  The Hubble Space Telescope reveals
    massive outflows of hot ionized gas through the red $H\alpha$ emission seen
    as gas is blasted out of the galaxy in a bipolar flow.}
\end{figure}

>>>>

\section{The Cosmological Context of Galaxy Formation}
The modern picture of galaxy formation sits within the context of a $\Lambda$
Cold Dark Matter  ($\Lambda CDM$) cosmology.  This is a universe which has a
no curvature, the majority of its mass-energy in a cosmological constant
$\Lambda$, and most of its matter in a collisionless form (Dark matter).  
Roughly $5\%$ of the universe exists as baryons, which began as a mostly
isothermal gas of hydrogen and helium.

The formation of galaxies within the universe began with the gravitational
collapse of small, linear density perturbations that were likely seeded by
quantum fluctuations amplified by inflation.  These perturbations grow through
gravitational collapse.  Until $z\sim1100$, only dark matter perturbations were
able to grow.  Prior to this, baryons were coupled to photons, causing density
perturbations to simply oscillate as stable sound waves.  This early collapse of
matter meant that when decoupling occured at $z\sim1100$.
\section{Numerical Simulations of Galaxies}
\section{The Importance of Feedback}
\begin{figure}
    \includegraphics[width=\textwidth]{M82.eps}
    \caption{Massive outflows in M82}{The evidence for feedback is no clearer
    than here in the Cigar Galaxy, M82.  The Hubble Space Telescope reveals
    massive outflows of hot ionized gas through the red $H\alpha$ emission seen
    as gas is blasted out of the galaxy in a bipolar flow.}
\end{figure}
